### 2019-10-27 Manuscript/manuscript.tex
progress on abstract

Laurentia was a major continent throughout the majority of the Proterozoic and is hypothesized to have had a central position in both the Paleoproterozoic Nuna and Neoproterozoic Rodinia supercontinents. The paleogeographic position of Laurentia is key to the development of reconstructions of Proterozoic paleogeography. There is a rich record of Precambrian paleomagnetic poles from Laurentia as well as an extensive geologic history of tectonism that are both key to evaluating and developing paleogeographic models. Data from the Slave and Superior provinces of Laurentia provide what is arguably the strongest evidence of differential plate tectonics

>>>>

Laurentia was a major continent throughout the majority of the Proterozoic and is hypothesized to have had a central position in both the Paleoproterozoic Nuna and Neoproterozoic Rodinia supercontinents. The paleogeographic position of Laurentia is key to the development of reconstructions of Proterozoic paleogeography. There is a rich record of Precambrian paleomagnetic poles from Laurentia as well as an extensive geologic history of tectonism that are both key to evaluating and developing paleogeographic models. Data from the Slave and Superior provinces of Laurentia provide what is arguably the strongest evidence of differential plate tectonics in the Rhyacian and Orosirian Periods of the Paleoproterozoic (2.3 to 1.8 Ga) leading up to their amalgamation through the Trans-Hudson orogeny that led to the formation of the core of Laurentia. Subsequent crustal growth proceeded through accretionary orogenesis until the rapid plate motion and continent-continent collision of the Grenvillian orogeny that was ongoing at the Mesoproterozoic-Neoproterozoic boundary at 1.0 Ga.
